The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-05 manuscript/manuscript.Rnw
show lower levels in PSG tree plot

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PSG1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=5)
@ 
\caption{Expression of pregnancy-specific glycoproteins}
\label{fig:psg_evolution_tree}
\end{figure}

>>>>

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PSG1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=1)
@ 
\caption{Expression of pregnancy-specific glycoproteins}
\label{fig:psg_evolution_tree}
\end{figure}
